---
title: "Data Wrangling Exercise 1"
author: Shafeeq Ur Rahaman
date: July 06 2017
output: html_document
---

```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r message=FALSE}
library(dplyr)
library(tidyr)
library(readr)
library(plyr)
library(magrittr)
```

####Requirement over here is to clean the dataset provided in order to make it easier to **visualize and analyze.**

# Step 0: Load the data in RStudio
####Loading the CSV file that needs to cleaned
```{r Load}
refine_original <- read.csv("refine_original.csv", header = TRUE)
```

# Step 1: Clean up brand names
####Cleaning the company column for misspellings 
```{r}
refine_original$company %<>% tolower()
refine_original %<>% mutate(company = replace(company, company %in% c('phillips','phllips','philips','phillps','fillips','phlips'), 'philips'))
refine_original %<>% mutate(company = replace(company, company %in% c('akzo','akz0','ak zo'), 'akzo'))
refine_original %<>% mutate(company = replace(company, company %in% c('unilver','unilever'), 'unilever'))
```

# Step 2: Separate Product Code and Number 
####Divide the **'Product.Code...Number'** variable into two new variables
```{r}
refine_original %<>% separate('Product.code...number', c("product_code","product_number"),sep = "-", remove=TRUE)
```

# Step 3: Adding new variable to the dataset
####Add Product Categories variable to the dataset that abbreviate the codes in product code variable.
```{r}
refine_original %<>% mutate(product_category = case_when(refine_original$product_code == 'p' ~ 'Smartphone', refine_original$product_code == 'v' ~ 'TV', refine_original$product_code =='x' ~ 'Laptop', refine_original$product_code == 'q' ~ 'Tablet'))
```

# Step 4: Add full address for geocoding
####Combine all three variables, address, city, country to form a new variable Full Address
```{r}
refine_original %<>% unite(full_address, c(address, city, country),sep = ',',remove=TRUE)
```

# Step 5: Create dummy variables for company and product category.
####Create dummy variables for company and product category as they are categorical variables.
```{r}
refine_original %<>% mutate(company_philips = (if_else(grepl(pattern='philips', x=refine_original$company), 1, 0)))
refine_original %<>% mutate(company_akzo = (if_else(grepl(pattern='akzo', x=refine_original$company), 1, 0)))
refine_original %<>% mutate(company_vanhouten = (if_else(grepl(pattern='van houten', x=refine_original$company), 1, 0)))
refine_original %<>% mutate(company_unilever = (if_else(grepl(pattern='unilever', x=refine_original$company), 1, 0)))
refine_original %<>% mutate(product_smartphone = (if_else(grepl(pattern='p', x=refine_original$product_code), 1, 0)))
refine_original %<>% mutate(product_laptop = (if_else(grepl(pattern='x', x=refine_original$product_code), 1, 0)))
refine_original %<>% mutate(product_TV = (if_else(grepl(pattern='v', x=refine_original$product_code), 1, 0)))
refine_original %<>% mutate(product_Tablet = (if_else(grepl(pattern='q', x=refine_original$product_code), 1, 0)))
```

# Step 6: Save as a new dataframe and submit on Github.
####Creating the cleaned file and submitting it into Github
```{r}
write.csv(refine_original, "refine_clean.csv")
```

