---
title: "Data Wrangling Exercise 2"
author: "Shafeeq Ur Rahaman"
date: "7/17/2017"
output: html_document
---
```{r message=FALSE}
library(tidyverse)
library(magrittr)
```
####Requirement over here is to clean the dataset provided in order to make it easier to **visualize and analyze.**

# Step 0: Load the data in RStudio
####Loading the CSV file that needs to cleaned
```{r echo=TRUE,message=FALSE}
titanic_original <- read_csv("titanic_original.csv", col_names = TRUE)
head(titanic_original)
```
# Step 1: Port of embarkation
####Replacing the missing values such as blank and empty string 
```{r}
titanic_original %<>% mutate(embarked = if_else(is.na(embarked), 'S', embarked))
titanic_original %>% select(embarked) %>% unique()
```
# Step 2: Age
####Replacing the missing values such as blank and empty string by calculating the mean of the age
```{r}
#titanic_original %<>% mutate(age = if_else(is.na(age), mean(age, na.rm = TRUE), age))
titanic_groupby_average <- titanic_original %>% 
                            group_by(pclass, sex) %>% 
                            summarise(meanage=mean(age, na.rm=TRUE))

titanic_original <- titanic_original %>% 
                     left_join(titanic_groupby_average, by=c("pclass","sex")) %>%
                     mutate(age=if_else(is.na(age), meanage, age)) %>% 
                     select(-meanage)

any(is.na(titanic_original$age))
  
```
# Step 3: Lifeboat
####Replacing the missing values such as blank and empty string by NA. But as read_csv function was used to load the dataset all missing values were already replaced by 'NA'
```{r}
any(is.na(titanic_original$cabin))

any(titanic_original$cabin=="", na.rm = TRUE)
```
# Step 4: Cabin
####Create a tracking column has_cabin_number so as can be used as a indicator of survival
```{r}
titanic_original$has_cabin_number <- if_else(is.na(titanic_original$cabin), 0, 1)
titanic_original
```

# Step 5: Save as a new dataframe and submit on Github.
####Creating the cleaned file and submitting it into Github
```{r}
write_csv(titanic_original,"titanic_clean.csv")
```




